%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[export]{adjustbox}
\usepackage{titlesec}

\titlelabel{$\circ$ } % clear the #.# for the subsection header
\newcommand\filledcirc{{\color{black}\bullet}\mathllap{\circ}}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-40pt}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%-------------------------
% Custom commands
\newcommand{\role}[2]{\item{\textbf{#1} \hfill #2 \\}} % job description
\newcommand{\station}[2]{#1  \hfill #2 \\} % employer/department
\newcommand{\project}[2]{\item\small{#1: #2}} % activity/ achievement

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\projectliststart}{\begin{itemize}[leftmargin=*] \vspace{-5pt} }
\newcommand{\projectlistend}{\end{itemize}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\addtolength{\tabcolsep}{4pt}    %spacing between columns
{\renewcommand{\arraystretch}{1} %spacing between rows
\begin{figure}[t]
	\centering
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} ll}
		\multicolumn{2}{l}{\textbf{{\Huge Nikolas Rieble}}}	\\
		\multicolumn{2}{l}{Software Engineer}	\\\\
		\begin{tabular}{ll}
			a: &Ungererstr. 161, 80805 Munich\\
			e: &nikolas-rieble@protonmail.com\\
			p: &+49 172 1811 209\\
			g: &github.com/nikolasrieble
		\end{tabular} &
		\begin{minipage}{0.6\textwidth}
			\section*{Profile}
			Experienced problem solver with a focus on value creation. I have a strong background in software engineering, data engineering and machine learning. I am passionate about building high-quality software and leading teams to success. I am a core maintainer of the recharts library and have experience in refactoring legacy code bases.
		\end{minipage}
	\end{tabular*}
\end{figure}
}


%-----------EXPERIENCE-----------------
\section{Work Experience}

\resumeSubHeadingListStart

\role{Senior Software Engineer II}{since Feb. 2024}
\station{HashiCorp}{}
\role{Engineering Manager}{Okt. 2023 - Jan. 2024}
\begin{itemize}
	\item Lead the refactoring of a deserted code base to a maintainable state, growing the team from 2 to 5 engineers
\end{itemize}
\role{Software Engineer III}{Mar. 2022 - Sep. 2023}
\begin{itemize}
	\item Lead the refactoring of a deserted code base to a maintainable state, growing the team from 2 to 5 engineers
	\item Reduced front end bundle size by 40\%, by replacing a core charting component, leading me into landing the position of core maintainer in recharts
	\item Architected the integration of machine learning features into the platform, enabling forecast and anomaly detection
\end{itemize}
\role{Software Engineer II}{Jul. 2021 - Feb. 2022}
\station{Tulip Interfaces}{}
\begin{itemize}
	\item Championed engineering best practice and cross-team collaboration by introducing code ownership to the engineering organisation and leading the engineering reading group
	\item Built caching OPC UA server data to enable users to search nodes, avoid redundant requests and improve customer experience
\end{itemize}
\role{Data Engineer}{Oct. 2019 - Jun. 2021}
\station{Scalable Capital}{}
\projectliststart
\project{Developing ETL pipelines with Airflow}{To extract data from multiple sources and conduct long-running daily OLAP queries, I implemented airflow jobs in Python.}
\project{Driving BI tool usage in the company}{Maintaining metabase as a self-service BI tool and educating colleagues across all departments.}
\project{Extracting data from a micro-service architecture}{Implementing event-driven message sending using AWS SQS and SNS from Java 8 and Kotlin applications.}
\projectlistend
\role{Fullstack IoT Developer}{Aug. 2018 - Sep. 2019}
\station{Hilti GmbH Industriegesellschaft für Befestigungstechnik}{}
\projectliststart
\project{Professional software development setup}{I increased development speed by setting up git and reduced communication overhead introducing and owning Atlassian Tools such as Jira, Confluence and Bamboo}
%\project{Smart Factory architecture}{Our team designed a modular system from data acquisition to reporting using multiple programming languages from Structured Text to C\#.}
%\project{Project Management}{I evaluated industry 4.0 use cases regarding their potential benefit and effort and consequently implemented those selected.}
\project{Data Warehousing}{I developed and maintained a Data Warehouse to align, clean and merge data from multiple databases and offer a single source of truth to end users.}
\project{Reporting}{I setup dashboards with PowerBI and educated key users from multiple departments to create and maintain their own reports.}
\project{Web App MVP}{To acquire data from production line workers, I implemented a web app with a html frontend and a javascript backend.}
\projectlistend

\resumeSubHeadingListEnd

 %-----------EDUCATION-----------------
 \section{Education}
\resumeSubHeadingListStart
\role{M.Sc. Computational Engineering Science}{Technical University of Berlin, 2015 - 2018}
\role{B.Sc. Psychology}{University of Vienna, 2013 - 2015}
\role{B.Sc. Mechanical Engineering}{Technical University Stuttgart, 2009 - 2014}
 \resumeSubHeadingListEnd

%--------PROJECTS------------
% \section{Projects}
%   \resumeSubHeadingListStart
%   	\item{\textbf{Computer Vision}: Random Ferns for Object Recognition in PolSAR radar images (Python)}
%   	\vspace{-0.1in}
%     \item{\textbf{Operations Research}: Processing Radioactive Waste in the US - A mathematical model (GAMS)}
%     \vspace{-0.1in}
% 	\item{\textbf{Robotics}: Reconstruction of a robots environment using the Kinect Camera (ROS, Python)}
% 	\vspace{-0.1in}
% \resumeSubHeadingListEnd

%--------Computer Literacy-------
% \section{Computer Literacy}
% \resumeSubHeadingListStart
% \item{\textbf{Programming}: Python (incl.: numpy, pandas, scipy, sklearn, pytorch), Kotlin, Java 8, C\#, Matlab, SQL, GAMS}
% \vspace{-0.1in}
% \item{\textbf{Dev Tools}: Sentry, Jenkins, Git, Bamboo, Jira}
% \vspace{-0.1in}
% \item{\textbf{Frameworks}: ROS, Apache Spark}
% \vspace{-0.1in}
% \resumeSubHeadingListEnd
\end{document}
